The Impact of Educational Expenses of New Coders

### 2021-04-21 outputs/paper/paper.Rmd
Edit model evaluation metrics

@@

```{r}
#### Beta ####
QuantPsyc::lm.beta(multiReg3)
```

@@

### VIF
car::vif(multiReg3)
### Tolerance
1/car::vif(multiReg3)
```

>>>>

# No correlation coefficient > 0.9 
# No multicollinearity
```

@@

```{r}
#### Beta ####
# TODO: create a bar plot to show which variable affects the most 
QuantPsyc::lm.beta(multiReg2)
QuantPsyc::lm.beta(multiReg3)
```

@@

### VIF
car::vif(multiReg2)
car::vif(multiReg3)

### Tolerance
1/car::vif(multiReg2)
1/car::vif(multiReg3)
```
